\papertitle

### 2014-03-18 final-report/paper.tex
Graphviz reference
Remove trailing spaces
Typo

\textbf{Graph Rendering:} We use D3 to render the \graph graph, which allows us to support various interactions and transistions. We use GraphViz \cite{graphviz} in the backend to generate graph layout information. GraphViz allows us to generate graph layouts that are optimized to minimize area footprint. The layout information is then fed into a D3-based rendering engine which supports various interactions and animations.

>>>>

\textbf{Graph Rendering:} We use D3 to render the \graph graph, which allows us to support various interactions and transitions. We use GraphViz \cite{Ellson01graphviz} in the backend to generate graph layout information. GraphViz allows us to generate graph layouts that are optimized to minimize area footprint. The layout information is then fed into a D3-based rendering engine which supports various interactions and animations.
